\Title

### 2019-12-20 source/tex/paper.tex
Updated to match version on arxiv
Updated to match version on arxiv.

\documentclass[a4paper,12pt]{article}
\usepackage[style=numeric,
            sorting=none,
            sortcites=true]{biblatex}
% \usepackage[style=numeric,
%             sorting=none,
%             sortcites=true,
%             bibencoding=ascii,
%             backend=biber]{biblatex}
\addbibresource{bibdata.bib}
\usepackage[dvipsnames]{xcolor}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{breqn}
% \usepackage[colorlinks=false]{hyperref}% for journals
\usepackage[colorlinks=true,citecolor=red]{hyperref}% for me
% \usepackage{showlabels}
% \usepackage{showkeys}
\usepackage{cdblatex}
\usepackage{geometry}
\usepackage{paper}

@@

@@

\begin{document}

\title{\bfseries Riemann Normal Coordinate expansions using Cadabra}
\author{%
Leo Brewin\\[10pt]%
School of Mathematical Sciences\\%
Monash University, 3800\\%
Australia}
% \date{10-Nov-2008}% 1st version started
% \date{29-Nov-2008}% 1st version finished
% \date{10-Mar-2009}% 1st version to gr-qc
% \date{22-Mar-2009}% minor corrections to section 8.2
% \date{09-Jul-2009}% minor grammatical corrections in response to 1st referee
% \date{12-Aug-2009}% small corrections arising from proofs received from CQG
\date{12-Aug-2009 (v1)\\
      19-Apr-2019 (v2)}% major changes to correct errors in 4th and higher order terms,
                       % all code will be available on github
\reference{Preprint: arXiv:0903.2087\\[5pt]
           Journal: {\it Class.Quantum.Grav.} {\bf 26} 175017 (2009)}

@@

\BegNote{\bf\large Version 2}
The first version of this paper was written in 2009. This second version (written in 2019)
differs from the first in a number of important ways. First, the discussion on Cadabra has
been completely rewritten to account for the revised syntax introduced in the latest version
of Cadabra (itself updated in 2016). Second, and more importantly, a significant
computational error in the first version has been corrected. Though the algorithms given in
the first version were correct their implementation in Cadabra (by this author) was
incorrect. This lead to errors first in the cubic and higher order terms in the generalised
connections and then, down the line, to computations built upon the generalised connections
(e.g., the initial and boundary value problem and the arc-length equations). The Cadabra
codes have been corrected and thoroughly cross-checked. A number of minor typographical
errors have also been corrected.
\EndNote

@@

All of the $\BigO{\eps^6}$ Cadabra programs were not overly demanding on computational
resources, taking between 0.5 second and 12 minutes to run and requiring
between 40 and 360 Mbyte of memory (on a Mac Pro running macOS 10.14.4).

The Cadabra codes and several support scripts are available from the author's GitHub site
\ \url{https://github.com/leo-brewin/cadabra-riemann-coords}.

@@

\begin{dgroup*}[compact,spread={3pt}]
   \dMath{11.3a}{-g(x)        = \cdb{Ndetg}     + \BigO{\eps^6}}{eqn:detg}{\hskip 1cm\hfill}
   \dMath{11.3b}{\sqrt{-g(x)} = \cdb{sqrtNdetg} + \BigO{\eps^6}}{eqn:sqrtdetg}{\hskip 1cm\hfill}
   \dMath{11.3c}{\log{-g(x)}  = \cdb{logNdetg}  + \BigO{\eps^6}}{eqn:logdetg}{\hfill}
\end{dgroup*}

@@

All of the Cadabra files used in preparing this paper are available at the GitHub repository
\ \url{https://github.com/leo-brewin/cadabra-riemann-coords}

>>>>

\pdfoutput=1% forces arxiv to use pdflatex
% --------------------------------------------------------------------------------------------
\def\Title{Riemann Normal Coordinate expansions using Cadabra.}
\def\Author{Leo Brewin}
% --------------------------------------------------------------------------------------------
\documentclass[a4paper,12pt]{article}
%
% biber will replace LaTeX accented characters like \'{e} with utf-8 characters.
% The utf-8 characters are written to the .bbl and this causes problems with pdflatex.
%    First  solution use: biber tutorial and \usepackage[latin1]{inputenc}
%    Second solution use: biber --decodecharsset=null tutorial
\usepackage[style=numeric, sorting=none, sortcites=true]{biblatex}
\addbibresource{bibdata.bib}
%
% \usepackage{showlabels}
% \usepackage{showkeys}
\usepackage{cdblatex}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{paper}

@@

% \usepackage[colorlinks=false]{hyperref}% for journals
% \usepackage[colorlinks=true,citecolor=red]{hyperref}% for me
\hypersetup{colorlinks=true,
            citecolor=blue,
            linkcolor=red,
            pdfauthor= \Author,
            pdftitle = \Title}

@@

% ============================================================================================
\begin{document}

\input{../cadabra/lib/export.cdbtex}% pulls in all the Cadabra results

\CdbSetup{action=verbatim}% we won't be processing any Cadabra code,
                          % just listing code from other sources

\lstset{numbers=left,gobble=2,basicstyle=\ttfamily\small,escapechar=|}

% ============================================================================================
\title{\Title}
\author{\Author\\[10pt]%
School of Mathematical Sciences\\%
Monash University, 3800\\%
Australia}
% \date{10-Nov-2008}% 1st version started
% \date{29-Nov-2008}% 1st version finished
% \date{10-Mar-2009}% 1st version to gr-qc
% \date{22-Mar-2009}% minor corrections to section 8.2
% \date{09-Jul-2009}% minor grammatical corrections in response to 1st referee
% \date{12-Aug-2009}% small corrections arising from proofs received from CQG
\date{12-Aug-2009 (v1)\\
      10-Dec-2019 (v2)}% major changes to correct errors in 4th and higher order terms,
                       % all code will be available on github
\reference{Preprint: arXiv:0903.2087\\[5pt]
           Journal: {\it Class.Quantum.Grav.} {\bf 26} 175017 (2009)}

@@

\BegNote{\bf\large Version 2}
The first version of this paper was written in 2009. This second version (written in 2019)
differs from the first in a number of important ways. First, the discussion on Cadabra has
been completely rewritten to account for the revised syntax introduced in the latest version
of Cadabra (itself updated in 2016)\footnote{The Cadabra results in this paper are based on
\CdbVersion}. Second, and more importantly, a significant computational error in the first
version (of this paper) has been corrected. Though the algorithms given in the first version
were correct their implementation in Cadabra (by this author) was incorrect. This lead to
errors first in the quartic and higher order terms in the generalised connections and then,
down the line, to computations built upon the generalised connections (e.g., the initial and
boundary value problem and the arc-length equations). The Cadabra codes have been corrected
and thoroughly cross-checked. A number of minor typographical errors have also been
corrected.
\EndNote

@@

All of the $\BigO{\eps^6}$ Cadabra programs were not overly demanding on computational
resources, taking between 0.5 second and 12 minutes to run and requiring
between 40 and 360 Mbyte of memory (on a Mac Pro (2013) running macOS 10.14.4).

The Cadabra codes and several support scripts are available from the author's GitHub site
\ \url{https://github.com/leo-brewin/riemann-normal-coords}.

@@

\begin{dgroup*}[compact,spread={3pt}]
   \dMath{11.3a}{-g(x)         = \cdb{Ndetg}     + \BigO{\eps^6}}{eqn:detg}{\hskip 1cm\hfill}
   \dMath{11.3b}{\sqrt{-g(x)}  = \cdb{sqrtNdetg} + \BigO{\eps^6}}{eqn:sqrtdetg}{\hskip 1cm\hfill}
   \dMath{11.3c}{\log{(-g(x))} = \cdb{logNdetg}  + \BigO{\eps^6}}{eqn:logdetg}{\hfill}
\end{dgroup*}

@@

All of the Cadabra files used in preparing this paper are available at the GitHub repository
\ \url{https://github.com/leo-brewin/riemann-normal-coords}
